---
title: "WWBI Graphs"
author: "Bureaucracy Lab"
date: "9 December, 2020"
output: html_document
---

```{r setup, include=FALSE}
library(plotly)
library(rmarkdown)
library(RColorBrewer)
knitr::opts_chunk$set(
  echo = FALSE, warning = FALSE, fig.width = 10, fig.height = 10)


wwbi_dat <- "C:/Users/WB551206/OneDrive - WBG/Documents/WB_data/wwbi"

load(file = file.path(wwbi_dat, "wwbi.Rdata"))

```

# Introduction

This document presents draft figures of the Worldwide Bureaucracy Indicators for potential use in future, public-facing digital mediums. In constructing the images, we prioritized user functionality and transparency. The figures contain features that most users expect nowadays from high-quality websites, including including hovertext and legend interactivity, as well as the ability to download the image directly from the browser. Furthermore, the figures use publicly-available data and can be reproduced with code from the WWBI GitHub [repository](https://github.com/worldbank/Worldwide-Bureaucracy-Indicators) so that researchers or more curious users can see eactly how the graphs were developed.



# Graphs 

## Figure 1
```{r}
f1
```

## Figure 2.1
```{r}
f2.1
```


## Figure 2.2
```{r}
f2.2
```

## Figure 2.3
```{r}
f2.3
```

## Figure 3
```{r}
f3
```

## Figure 4
```{r, fig.height=18} 
hmp
```

Note: The figure presents the ratio of public sector wages for specific occupations within a country to the global median – taken as 1.  Ratio’s above 1 indicate a cross-country premium for the indexed occupation compared to the global median (shaded X) while ratio’s below 1 indicate a negative cross-country premium (shaded Y). Blank cells show no available data.
